---
title: "Lab 02: Data wrangling"
Date: "Wenesday, March 15"
author: "Layal H. Ghryani"
date: "Oct 11th 2023"
editor_options: 
  chunk_output_type: console
output:
  pdf_document: default
  html_document: default
---

# Packages

```{r load-packages, message = FALSE}
library(tidyverse)
```

# Data

```{r load-data, message = FALSE}
lego <- read_csv("lego.csv")
```

# Exercise 1
```{r}
lego <- lego %>% filter(pieces > 0) %>% filter(!is.na(year)) %>% 
  filter(!is.na(retail_price))  %>% filter (retail_price != 0)
# %>% Pipe it to the one before 
``` 
way 1:
lego_filtered <- lego %>% 
filter(!is.na(pieces)) %>%
filter(pieces != 0) %>%
filter(!is.na(retail_price)) %>%
filter(retail_price != 0) %>%
filter(!is.na(year))

way 2 :
lego <- filter(lego, pieces > 0)
lego <- filter(lego,!is.na(year))
lego <- filter(lego,!is.na(retail_price))
lego <- filter(lego,retail_price != 0)
testing <- filter(lego,retail_price == 0)


# Exercise 2
```{r}
lego2 <- arrange(lego,desc(retail_price)) %>% slice(1:3) #desc = descending order 

```

Another way:
lego_filtered % > %
arrange(desc(retail_price)) % > %
slice(1:3)%>%
print(width = Inf)

Describe the three most expensive sets here. 
the most expensive 3 lego sets are Millennium Falcon which costs 800\$ and
has 7541 pieces, 
the second most expensive set is Connections Kit which costs 755\$ 
and has 2455 pices, the third most expensive set is Death Star whcih costs 500\$
and contains 4016 pieces. 

# Exercise 3
```{r}
lego <- mutate(lego,price_per_piece = retail_price/pieces)
```

# Exercise 4
```{r}
lego4<-lego %>% arrange(desc(price_per_piece)) %>% slice(1:5) %>%
  select(name,themegroup,theme,pieces,price_per_piece) 
```
another way:
lego %>%
  arrange(desc(price_per_piece)) %>%
  slice(1:5) %>% 
  select(name, themegroup, theme, pieces, price_per_piece)
  
Describe what you notice about the sets with the highest price per piece. 
The highest prices are the sets consisting of 1 piece only. 

# Exercise 5
```{r}
lego5 <- lego %>% filter(theme == "The Lord of the Rings") %>%
  group_by(subtheme) %>% summarise(maximum=max(retail_price),minimum=min(retail_price),
                                   count = n())
```

# Exercise 6

```{r}
lego6 <- group_by(lego, year)
yearly_trends <- summarize(lego6, setsNumber = n(),
                      price_per_piece_median = median(price_per_piece))
```

# Exercise 7

```{r}
library(ggplot2)
ggplot(data=yearly_trends, mapping=aes(x=price_per_piece_median, 
                                       y=year, size = setsNumber)) + 
  geom_point() + 
  labs(title = "Yearly trend of price per piece according to number of sets") 
```

Comment on what you observe in the plot above. 
The size of the sets increasing over the years.